Extreme Value Chapter 3

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
what am I even doing?

```{r fig.height=6, fig.width=12}

corr_a %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
  theme_bw() +
  # scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> a

corr_b %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
  theme_bw() +
  # scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> b

>>>>

```{r fig.height=4, fig.width=12}

corr_a %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
  theme_bw() +
  # scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> a

corr_b %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp, nrow=1) +
  geom_hline(yintercept = 0, color = "red") +
  geom_boxplot(alpha = 0.9) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
  theme_bw() +
  # scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> b
